---
title: "R Notebook"
output: html_notebook
---


A closer look at the H1b visas from 2011 to 2016. This is an interesting data set because of the latitudes and longitudes and what we can learn from locations.    
   
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(maps)
```   


because this is suck a large data set I would take the time to get a test of what read code is faster. I will compare read.csv with stringAsFactors = FALSE and read_csv from the readr package.   
```{r}
system.time(visa <- read.csv("h1b_kaggle.csv", stringsAsFactors = FALSE))
system.time(visa <- read_csv("h1b_kaggle.csv", ))

```
This is a large data set 3002458 rows read_csv read the 469 MB into R in 8.39 seconds, it also shows the types avoiding having to call str(). It takes the standard read.csv 49.353 seconds so this over a 5X speed increase.     
   
I would like to see the top 20 companies that are sponsoring H1B visas.   
```{r}
top_employers <- visa %>% group_by(EMPLOYER_NAME) %>% 
                          summarise(count = n(), percent = round(count*100/nrow(visa), 2)) %>%
                          arrange(desc(count)) %>%
                          top_n(20, wt = count) 

ggplot(top_employers, aes(x = reorder(EMPLOYER_NAME, percent),
                                y = percent, fill = EMPLOYER_NAME)) + 
                      geom_bar(stat = "identity")  +
                      geom_text(aes(label = percent), vjust = 1, hjust = .5) + 
                      labs(x = "EMPLOYER_NAME", y = "Petitions Made(in percentage)") +  
                      theme(legend.position = "none") +
                      coord_flip()
```   
This is the top only the top so making up `r sum(top_employers$percent)` percent of all the employers with H1B visa.
   
      
Lets take a look and why the most H1Bs are working. 
```{r}
visa <- visa %>% separate(WORKSITE, c("city", "state"), ",") %>% arrange(state)

by_state <- visa %>% group_by(state) %>% 
                     summarise(count = n(), percent = round(count*100/nrow(visa),2)) %>% 
                     arrange(desc(count)) %>% 
                     top_n(20, wt = count)


ggplot(by_state, aes(x = reorder(state, percent),
                                y = percent, fill = state), main = "Precent by state") +
                  geom_bar(stat = "identity") +
                  geom_text(aes(label = percent), vjust = 1, hjust = .5) +
                  labs(x = "State") +
                  theme(legend.position = "none") +
                  coord_flip()


```   
Here we can see that the top 3 states California, New York and Texas, are also the states with the largest populations and the largest GDPs in the United States.   
    
```{r}
by_city <- visa %>% group_by(city) %>% 
                     summarise(count = n(), percent = round(count*100/nrow(visa),2)) %>% 
                     arrange(desc(count)) %>% 
                     top_n(20, wt = count)


ggplot(by_city, aes(x = reorder(city, percent),
                                y = percent, fill = city), main = "Precent by state") +
                  geom_bar(stat = "identity") +
                  geom_text(aes(label = percent), vjust = 1, hjust = .5) +
                  labs(x = "City") +
                  theme(legend.position = "none") +
                  coord_flip()
```   
Looking at the cities that are in the top 20 it is the same the largest population in the USA is New York is number 1 Houston is number 4 and San Francisco is number 14. The top 5 New York, Houston, San Francisco, Atlanta and Chicogo are also on a list of cities with the highest GDP in the United States.   
   
      
Lets see what kind of jobs are being done by H1Bs.   
```{r}
jobs <- visa %>% group_by(JOB_TITLE) %>% 
                     summarise(count = n(), percent = round(count*100/nrow(visa),2)) %>% 
                     arrange(desc(count)) %>% 
                     top_n(20, wt = count)

ggplot(jobs, aes(x = reorder(JOB_TITLE, percent),
                                y = percent, fill = JOB_TITLE), main = "Precent by state") +
                  geom_bar(stat = "identity") +
                  geom_text(aes(label = percent), vjust = 1, hjust = .5) +
                  labs(x = "Job Title") +
                  theme(legend.position = "none") +
                  coord_flip()
```   
   
The top three are computer programmers, this is interesting because of all the news saying that programing was being done overseas, it is also a good sign that there are that many jobs that need to be filled. 








